### 2023-03-28 resilience-safe-down.tex
Brouillon 3point4

>>>>

\begin{theorem}
The resilience problem is decidable for WSTS with 
%	more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
\textcolor{red}{
additional hypothesis.
}
\end{theorem}

\begin{proof}
Let $\{J_1, J_2,...,J_n\}$ be the ideal decomposition of $\Safe$ and $\{b_1,b_2,...,b_m\}$ be the (unique) minimal basis of $\Bad$.

Let's assume for now for simplicity's sake that $\Bad = \uparrow \{b\}$

As an hypothesis, we assume that $\pred^*(\Safe)$ is downward closed as well.
And let $\{J'_1, J'_2,...,J'_n\}$ be the ideal decomposition of $\pred^*(\Safe)$.

Resilience asks whether 
$ \uparrow \{b\} \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$.

Of note is that $ \downarrow \{b\} \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$
if and only if
there exists some $i$ such that
$\downarrow \{b\} \subseteq J'_i$.

\mathieu{Try and find a condition under which "$ \uparrow \{b\} \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$?" is decidable and/or find an undecidable problem that reduce to a variation on 
"$\uparrow \{b\} \subseteq J'_i$ ?"}
\end{proof}
